### 2018-04-30 Paper/bg.tex
work in progress ...

In this section, we provide a brief theoretical background to the
derivative-based global sensitivity measure and the polynomial chaos
expansion.

\subsection{Derivative-based global sensitivity}

The derivative-based global sensitivity analysis (DGSA) is performed by 
estimating a sensitivity measure~\cite{Sobol:2009} for each stochastic
parameter in a model or a function. The
sensitivity measure associated with a parameter, $\theta_i$, based on
the observable, $\mathcal{Y}$ is given as follows:

\be
\mu_i = \mathbb{E}\left[\left(\frac{\partial \mathcal{Y}(\bm{x})}{\partial \theta_i}\right)^{2}\right]
\label{eq:mu}
\ee

\noindent The derivative in the above equation is estimated using finite
difference as given below, and averaged using pseudo-random samples in
the uncertain parameter domain.

@@

The total number of model realizations or function evaluations
needed to
compute $\mu_i$ in a Euclidian space $\mathbb{R}^d$ using $N$ samples is
therefore, $N\times(d+1)$. The derivative in Eq.~\ref{eq:partial} could be evaluated
analytically in case the functional dependence of $\mathcal{Y}$ and $\theta_i$
is known. Note that the perturbation $\Delta\theta_i^{*}$ is extremely small 
compared to the uncertainty in $\theta_i$ which leads to a significant improvement
over the `elementary effect' of a parameter, estimated in the Morris method~\cite{Morris:1991}
using large increments.

@@

\be
\mathcal{T}(\theta_i) \leq \frac{\mathcal{C}_i\mu_i}{V}~(\propto \hat{\mathcal{C}_i\mu_i})
\label{eq:bound}
\ee

\noindent The upper bound in the above inequality is proportional to the product of $\mathcal{C}_i$
and $\mu_i$. However, for the purpose of parameter screening as discussed later in
Section~\ref{sec:method}, we consider a normalized product, $\hat{\mathcal{C}_i\mu_i}$:

\be
\hat{\mathcal{C}_i\mu_i} = \frac{\mathcal{C}_i\mu_i}{\sum_i \mathcal{C}_i\mu_i}
\label{eq:cmu}
\ee

>>>>

In this section, we introduce the notations used in the rest of
the article, and present the requisite background material on 
derivative-based global sensitivity measures and surrogate modeling 
using polynomial chaos expansion.

\subsection{Derivative-based global sensitivity analysis}  
Let $\mathcal{Y}$ be a mathematical model that is a function of $\Np$ uncertain 
parameters, $\theta_1, \theta_2, \ldots, \theta_\Np$. The goal of sensitivity analysis
is measuring the influence of each component of the parameter vector 
$\bm{\theta}$ on the model output. 
\alennote{We consider the case of statistically independent parameters, right? 
Should we make this precise?}
Derivative-based global sensitivity analysis (DGSA) is performed by 
computing derivative based global sensitivity measures (DGSMs)~\cite{Sobol:2009} 
for each uncertain parameter in the model. 
Specifically, we consider the following DGSMs, 
\be
\mu_i = 
\mathbb{E}\left[\left(\frac{\partial \mathcal{Y}(\bm{\bm{\theta}})}{\partial \theta_i}\right)^{2}\right], \quad i = 1, \ldots, \Np.
\label{eq:mu}
\ee
Here $\mathbb{E}$ denotes expectation over the uncertain parameters.
Notice that this formulation assumes that the function $\mathcal{Y}$ is differentiable
with respect to $\theta_i$, $i = 1, \ldots, \Np$, almost surely.

The derivative in the above equation can be estimated using finite
differences as given below, and averaged using Monte Carlo sampling in
the uncertain parameter space.

@@

The total number of model realizations or function evaluations
needed to
compute $\mu_i$ in a Euclidian space $\mathbb{R}^d$ using $N$ samples is
therefore, $N\times(d+1)$. The derivative in Eq.~\ref{eq:partial} could be evaluated
analytically in case the functional dependence of $\mathcal{Y}$ and $\theta_i$
is known. Note that the perturbation $\Delta\theta_i^{*}$ is extremely small 
compared to the uncertainty in $\theta_i$ which leads to a significant improvement
over the `elementary effect' of a parameter, estimated in the Morris method~\cite{Morris:1991}
using large increments.  It is noted by many authors~[REFS], and also observed
in the numerical experiments in the present work, that a modest Monte Carlo
sample size is often sufficient for computing~\eqref{eq:mu} with reasonable
accuracy.

@@

\be
\mathcal{T}(\theta_i) \leq \frac{\mathcal{C}_i\mu_i}{V}~(\propto \widehat{\mathcal{C}_i\mu_i})
\label{eq:bound}
\ee

\noindent The upper bound in the above inequality is proportional to the product of $\mathcal{C}_i$
and $\mu_i$. However, for the purpose of parameter screening as discussed later in
Section~\ref{sec:method}, we consider a normalized product, $\widehat{\mathcal{C}_i\mu_i}$:

\be
\widehat{\mathcal{C}_i\mu_i} = \frac{\mathcal{C}_i\mu_i}{\sum_i \mathcal{C}_i\mu_i}
\label{eq:cmu}
\ee
